\Large \bf Vigor: Toward Carrier-Grade Software Network Functions

### 2016-10-27 doc/paper/paper.tex
Fix the ring implementation in the original code version of the example.

This section motivates and explains at a high level what it's like to use Vigor when developing NFs. For the sake of illustration, say we wish to develop a trivial stateful NF that implements the discard protocol~\cite{rfc863}: an infinite loop receives packets from one interface, discards the ones that go to port 9 (``discard port''), and forwards the others through another interface.

@@

int main() {
  struct packet packets[CAP] = {};
  int begin = 0, end = 0;

  while(1) {
    if (end != (begin - 1) || 
        !(end == CAP - 1 && begin == 0)) {
      if (receive_packet(&packets[end]) && 
          packets[end].port != 9)
        end = (end + 1)%CAP;
    }
    if (end != begin && can_send_packet()) {
      send_packet(&packets[begin]);
      begin = (begin + 1)%CAP;
    }
  }
  return 0;
}
\end{lstlisting}
  \caption{Original implementation of the Drop protocol}
  \label{lst:orig}
\end{figure}

>>>>

This section motivates and explains at a high level what it's like to use Vigor when developing NFs. For the sake of illustration, say we wish to develop a trivial stateful NF that implements the discard protocol~\cite{rfc863}: an infinite loop receives packets from one interface, discards the ones that target port 9 (``discard port''), and forwards the others through another interface.

@@

int main() {
  struct packet packets[CAP] = {};
  int begin = 0, queue_len = 0;

  while(1) {
    if (queue_len < CAP) {
      int end = (begin + queue_len)%CAP;
      if (receive_packet(&packets[end]) &&
          packets[end].port != 9)
        queue_len += 1;
    }
    if (0 < queue_len) {
      send_packet(&packets[begin]);
      begin = (begin + 1)%CAP;
    }
  }
  return 0;
}
\end{lstlisting}
  \caption{Original implementation of the Drop protocol}
  \label{lst:orig}
\end{figure}
